02_limma_hyp

### 2019-03-19 scripts/02_limma_hyp.Rmd
remove kable tables

printplotcontrasts <- function(whichcontrast){
  cont <- whichcontrast
  summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
  print(kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1))
  print(plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main=whichcontrast, frame.plot=F))
}

>>>>

printplotcontrasts <- function(whichcontrast){
  cont <- whichcontrast
  print(summary(decideTestsDGE(
    glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
    adjust.method="fdr", p.value=0.01)))
  print(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
  print(plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main=whichcontrast, frame.plot=F))
}
